---
title: "T-rjd3workspace-refresh"
format: html
---

```{r}
#| label: loading-rjdverse
#| echo: true
#| eval: true
library("rjd3toolkit")
library("rjd3workspace")
```

# Objectifs

- key reproducible format of testing (pre-vignette)
- the vignette

- end up with updated Fatih code and verif results in rjd3ws (not here)

- refresh data : TS, voir pour toutes policies + metadata ?

- idem fonction jsap_refresh

soupçon: fonctionne sur 1er sap 

pb practicité réinjection dans ws ?

## next: cas outliers / outliers_stoch

- pb period, end, start 

- jsap_refresh: issue to do !! understand what happens

- all, data, none (LATER ?), pas tarder si JP s'y met 

- balayer issues battle plan 

### Missing doc 

jws_add(jws, jsap)



## recap JP questions 

- current: issue ok 

- period, start end with outliers : issue ok

- jsap_refresh: issue ok  num 126

- all, data, none (LATER ?), pas tarder si JP s'y met 


### answered but to do 

- data all none:ok 

- vider cache: à integrer 

- compute à integrer 



## general 

- harmonize policies names 




## Issues

- policy current not available yet : take out of doc fort the moment : issue set up 

# Load and Read a Workspace
```{r}
#| echo: true
#| eval: true

library("rjd3toolkit")
library("rjd3workspace")
# file <- "C:/Users/YWYD5I/Documents/00_RJD3_Developpement/RJD3_development/Workspaces/rjd3workspace_refresh_test_GUI.xml"

file <- system.file("workspaces", "workspace_test_refresh.xml", package = "rjd3workspace")
jws <- jws_open(file)
# Read workspace
rws <- read_workspace(jws, compute= TRUE)
rws$processing$`SAProcessing-1`$`RF0811`$ts
rws$processing$`SAProcessing-1`$`RF0811`$referenceSpec
rws$processing$`SAProcessing-1`$`RF0811`$estimationSpec
rws$processing$`SAProcessing-1`$`RF0811`$resultSpec
rws$processing$`SAProcessing-1`$`RF0811`$results
summary(rws$processing$`SAProcessing-1`$`RF0811`$results)

rws$processing$`SAProcessing-2`$`RF0811`$referenceSpec # pb outliers is enabled no
rws$processing$`SAProcessing-2`$`RF0811`$estimationSpec
rws$processing$`SAProcessing-2`$`RF0811`$resultSpec 
# 5 pre specifed detecté et que 3 declarés
rws$processing$`SAProcessing-2`$`RF0811`$results
summary(rws$processing$`SAProcessing-2`$`RF0812`$results)


```

### Issues 

- print dans seats spec (should see all the changeable parameters)

forecasts 
backcasts 

- print seats dans results : idem 

# Refresh 

## Default option 

```{r}
# file <- "C:/Users/YWYD5I/Documents/00_RJD3_Developpement/RJD3_development/Workspaces/rjd3workspace_refresh_test_GUI.xml"

library("rjd3workspace")

file <- system.file("workspaces", "workspace_test_refresh.xml", package = "rjd3workspace")
jws <- jws_open(file)
jws_compute(jws)
jws_refresh(jws)

# v<-jws_refresh(jws, policy = "Complete")
# v NULL
## check refresh in R
# sap 1 ok
rws2 <- read_workspace(jws, compute= TRUE)
rws2$processing$`SAProcessing-1`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-1`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-1`$`RF0811`$resultSpec # outliers notés pre specified alors qu'ils ne le sont pas: en fait si dans la result spec 
rws2$processing$`SAProcessing-1`$`RF0811`$results
summary(rws2$processing$`SAProcessing-1`$`RF0811`$results)


# sap 2 (pas refresh)
rws2$processing$`SAProcessing-2`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-2`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-2`$`RF0811`$resultSpec 
# result spec pas reestimée ??
rws2$processing$`SAProcessing-2`$`RF0811`$results
```

### Issues NONE

- is default parameters ok



## Complete

### WS

```{r}
# file <- "C:/Users/YWYD5I/Documents/00_RJD3_Developpement/RJD3_development/Workspaces/rjd3workspace_refresh_test_GUI.xml"

library("rjd3workspace")

file <- system.file("workspaces", "workspace_test_refresh.xml", package = "rjd3workspace")
jws <- jws_open(file)
jws_compute(jws)

jws_refresh(jws, policy = "Complete")
# v<-jws_refresh(jws, policy = "Complete")
# v NULL
## check refresh in R
# sap 1 ok
rws2 <- read_workspace(jws, compute= TRUE)
rws2$processing$`SAProcessing-1`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-1`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-1`$`RF0811`$resultSpec # outliers notés pre specified alors qu'ils ne le sont pas: en fait si dans la result spec 
rws2$processing$`SAProcessing-1`$`RF0811`$results
summary(rws2$processing$`SAProcessing-1`$`RF0811`$results)


# sap 2 (pas refresh)
rws2$processing$`SAProcessing-2`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-2`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-2`$`RF0811`$resultSpec 
# result spec pas reestimée ??
rws2$processing$`SAProcessing-2`$`RF0811`$results
summary(rws2$processing$`SAProcessing-2`$`RF0811`$results)
```


### Issues: SPAN : setup 

- summary : lack series span and model span 



### SAP (LATER) 


```{r}
library("rjd3workspace")
file <- system.file("workspaces", "workspace_test_refresh.xml", package = "rjd3workspace")
jws <- jws_open(file)
jws_compute(jws)
sap1<-jws_sap(jws,1)
jsap_refresh(sap1, policy = "Complete")
sap_r<-jsap_refresh(sap1, policy = "Complete") 


##ISSUE diff return
# pas pratique car on est obligé de sortir le sap et de le re rentrer

jws_r<-jws_new()
# reinjecter dans we ?
jws_add(jws_r,sap_r)


## check refresh in R
# sap 1 ok
rws2 <- read_workspace(jws_r, compute= TRUE)
rws2$processing$`SAProcessing-1`
rws2$processing$`SAProcessing-1`$`RF0811 (frozen`()
rws2$processing$`SAProcessing-1`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-1`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-1`$`RF0811`$resultSpec
# outliers notés pre specified alors qu'ils ne le sont pas ?
summary(rws2$processing$`SAProcessing-1`$`RF0811`$results)

# sap 2
rws2$processing$`SAProcessing-2`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-2`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-2`$`RF0811`$resultSpec # result spec pas reestimée ??
rws2$processing$`SAProcessing-2`$`RF0811`$results



```


### Issues: pb return 

return different jsap_refresh et jws refresh 

- second or 3rd sap not refeshed 


## Fixed 

### WS

```{r}
# file <- "C:/Users/YWYD5I/Documents/00_RJD3_Developpement/RJD3_development/Workspaces/rjd3workspace_refresh_test_GUI.xml"

library("rjd3workspace")

file <- system.file("workspaces", "workspace_test_refresh.xml", package = "rjd3workspace")
jws <- jws_open(file)
jws_compute(jws)

jws_refresh(jws, policy = "Fixed")
# v<-jws_refresh(jws, policy = "Complete")
# v NULL
## check refresh in R
# sap 1 ok
rws2 <- read_workspace(jws, compute= TRUE)
rws2$processing$`SAProcessing-1`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-1`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-1`$`RF0811`$resultSpec 
rws2$processing$`SAProcessing-1`$`RF0811`$results
summary(rws2$processing$`SAProcessing-1`$`RF0811`$results)
# sap 2
rws2$processing$`SAProcessing-2`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-2`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-2`$`RF0811`$resultSpec # result spec pas reestimée ??
rws2$processing$`SAProcessing-2`$`RF0811`$results
```

### Issues: print 

- print in seats, outliers not FIXED, issue set up !





## FixedParameters
### WS

```{r}
file <- "C:/Users/YWYD5I/Documents/00_RJD3_Developpement/RJD3_development/Workspaces/rjd3workspace_refresh_test_GUI.xml"

jws <- jws_open(file)
jws_compute(jws)
jws_refresh(jws, policy = "FixedParameters")
# v<-jws_refresh(jws, policy = "Complete")
# v NULL
## check refresh in R
# sap 1 ok
rws2 <- read_workspace(jws, compute= TRUE)
rws2$processing$`SAProcessing-1`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-1`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-1`$`RF0811`$resultSpec 
rws2$processing$`SAProcessing-1`$`RF0811`$results
summary(rws2$processing$`SAProcessing-1`$`RF0811`$results)
# sap 2
rws2$processing$`SAProcessing-2`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-2`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-2`$`RF0811`$resultSpec # result spec pas reestimée ??
rws2$processing$`SAProcessing-2`$`RF0811`$results



```

### Issues 

-with seats outliers not INITIAL : issue set up 



## FixedAutoRegressiveParameters

### WS

```{r}
# file <- "C:/Users/YWYD5I/Documents/00_RJD3_Developpement/RJD3_development/Workspaces/rjd3workspace_refresh_test_GUI.xml"

library("rjd3workspace")

file <- system.file("workspaces", "workspace_test_refresh.xml", package = "rjd3workspace")
jws <- jws_open(file)
jws_compute(jws)

jws_refresh(jws, policy = "FixedAutoRegressiveParameters")
## check refresh in R
# sap 1 ok
rws2 <- read_workspace(jws, compute= TRUE)
rws2$processing$`SAProcessing-1`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-1`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-1`$`RF0811`$resultSpec 
rws2$processing$`SAProcessing-1`$`RF0811`$results
summary(rws2$processing$`SAProcessing-1`$`RF0811`$results)
# sap 2
rws2$processing$`SAProcessing-2`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-2`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-2`$`RF0811`$resultSpec # result spec pas reestimée ??
rws2$processing$`SAProcessing-2`$`RF0811`$results
summary(rws2$processing$`SAProcessing-2`$`RF0811`$results)


```



### Issues 

- outlier print not (INITIAL)in TS vs X13: issue set up 

- x13, auto reg param not reestimated (written in estimation spec): OK mais MA non plus ...
- TS idem 


## FreeParameters

### WS

```{r}
# file <- "C:/Users/YWYD5I/Documents/00_RJD3_Developpement/RJD3_development/Workspaces/rjd3workspace_refresh_test_GUI.xml"

library("rjd3workspace")

file <- system.file("workspaces", "workspace_test_refresh.xml", package = "rjd3workspace")
jws <- jws_open(file)
jws_compute(jws)

jws_refresh(jws, policy = "FreeParameters")
## check refresh in R
# sap 1 ok
rws2 <- read_workspace(jws, compute= TRUE)
rws2$processing$`SAProcessing-1`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-1`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-1`$`RF0811`$resultSpec 
rws2$processing$`SAProcessing-1`$`RF0811`$results
summary(rws$processing$`SAProcessing-1`$`RF0811`$results)
# sap 2
rws2$processing$`SAProcessing-2`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-2`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-2`$`RF0811`$resultSpec # result spec pas reestimée ??
rws2$processing$`SAProcessing-2`$`RF0811`$results



```



### Issues 


- les coeffs arima sont ecrits dans l'estimation spec comme s'ils n'allaient pas etre reestimés mais le sont 
Issue set up








## Outliers

### WS

```{r}
# file <- "C:/Users/YWYD5I/Documents/00_RJD3_Developpement/RJD3_development/Workspaces/rjd3workspace_refresh_test_GUI.xml"

library("rjd3workspace")

file <- system.file("workspaces", "workspace_test_refresh.xml", package = "rjd3workspace")
jws <- jws_open(file)
jws_compute(jws)

jws <- jws_open(file)
# Read current workspace
rws <- read_workspace(jws, compute= TRUE)
rws$processing$`SAProcessing-1`$`RF0811`$ts
rws$processing$`SAProcessing-1`$`RF0811`$referenceSpec
rws$processing$`SAProcessing-1`$`RF0811`$estimationSpec
rws$processing$`SAProcessing-1`$`RF0811`$resultSpec
rws$processing$`SAProcessing-1`$`RF0811`$results
summary(rws$processing$`SAProcessing-1`$`RF0811`$results)

# refresh
jws_refresh(jws, policy = "Outliers")
jws_refresh(jws, policy = "Outli",start=c(2020,1))ers


jws_refresh(jws, policy = "Outliers", period=12, start=c(2020,4))

jws_refresh(jws, policy = "Outliers", period=12, start=c(2020,4), end=c(2020,5))


jws_refresh(jws, policy = "Outliers", period=12, start=c(2020,1), end=c(2020,4))

jws_refresh(jws, policy = "Outliers", period=12, end=c(2020,4))

## Read refreshed workspace
# sap 1 ok
rws2 <- read_workspace(jws, compute= TRUE)
rws2$processing$`SAProcessing-1`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-1`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-1`$`RF0811`$resultSpec 
rws2$processing$`SAProcessing-1`$`RF0811`$results
summary(rws2$processing$`SAProcessing-1`$`RF0811`$results)
# sap 2
rws2$processing$`SAProcessing-2`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-2`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-2`$`RF0811`$resultSpec # result spec pas reestimée ??
rws2$processing$`SAProcessing-2`$`RF0811`$results
summary(rws2$processing$`SAProcessing-2`$`RF0811`$results)


```



### Issues 

- outliers pas effacés à partir du start 

- dans le print les ordre du modele arima sont reinitilaisés meme si pas stochastic componenet, coeffs modele reg arima reviennent bien à zero: OK if 


- Detection span: From 2100-01-01

#### Error on period to be added

#### Confus












## Outliers_StochasticComponent

### WS

```{r}
file <- "C:/Users/YWYD5I/Documents/00_RJD3_Developpement/RJD3_development/Workspaces/rjd3workspace_refresh_test_GUI.xml"

jws <- jws_open(file)
jws_compute(jws)
jws_refresh(jws, policy = "Outliers_StochasticComponent", period=12, end=c(2020,4))
## check refresh in R
# sap 1 ok
rws2 <- read_workspace(jws, compute= TRUE)
rws2$processing$`SAProcessing-1`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-1`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-1`$`RF0811`$resultSpec 
rws2$processing$`SAProcessing-1`$`RF0811`$results
summary(rws2$processing$`SAProcessing-1`$`RF0811`$results)
# sap 2
rws2$processing$`SAProcessing-2`$`RF0811`$referenceSpec
rws2$processing$`SAProcessing-2`$`RF0811`$estimationSpec
rws2$processing$`SAProcessing-2`$`RF0811`$resultSpec # result spec pas reestimée ??
rws2$processing$`SAProcessing-2`$`RF0811`$results
summary(rws2$processing$`SAProcessing-2`$`RF0811`$results)


```



### Issues 

- outliers pas effacés à partir du start 
- orders eet coeffs modele reg arima reviennent bien à zero
- Detection span: From 2100-01-01

- si on met end 

















