---
title: "T-rj3x13_ts_refresh_tests"
format: html
---

# Objectifs

- key reproducible format of testing (pre-vignette)
- the vignette

- end up with updated Fatih code and verif results in rjd3ws (not here)

## general 

- harmonize policies names 

## recap JP questions 

## o1: one refresh qmd per concerned package 

- with issues



```{r}
#| label: loading-rjdverse
#| echo: true
#| eval: true
library("rjd3toolkit")
library("rjd3x13")

```


```{r}
#| label: data import 
#| echo: true
#| eval: true
# Data  :
ipi <- read.csv2(
    "C:/Users/YWYD5I/Documents/00_RJD3_Developpement/RJD3_development/Data/IPI_nace4.csv"
)
ipi$date <- as.Date(ipi$date, format = "%d/%m/%Y")
ipi[, -1] <- sapply(ipi[, -1], as.numeric)
# creating a TS object from a data frame
y_raw <- ts(
    ipi[, "RF0812"],
    frequency = 12,
    start = c(1990, 1),
    end = c(2021, 12)
)
y_new <- ts(
    ipi[, "RF0812"],
    frequency = 12,
    start = c(1990, 1),
    end = c(2022, 9)
)

# start(y_raw)
end(y_raw)
# start(y_new)
end(y_new)

## add points for outlier detection 
window(y_new,start=c(2022,3), end=c(2022,5))<-c(51,52,53)


```


# Policies with span clean up 

## first estimation and spec to be refreshed

```{r}
# specification for first estimation
spec_x13_1 <- x13_spec("rsa5c")
spec_x13_1 <-add_outlier(spec_x13_1, type = "AO",
                         date = c("2020-03-01","2020-04-01"))

# first estimation
sa_x13 <- x13(y_raw, spec_x13_1) # AO (2000,6) and TD (2000,7)
sa_x13

# def of specs to refresh

current_result_spec <- sa_x13$result_spec
reference_spec <- sa_x13$estimation_spec

```


## test of period, start end parameters 

### Current

```{r}
#| echo: true
#| eval: false
spec_x13_ref <- x13_refresh(
    current_result_spec, # point spec to be refreshed
    reference_spec, # domain spec (set of constraints)
    period=12,
    start=c(2020,1),
    end = c(2021,12),
    policy = "Current")
spec_x13_ref
sa_x13_ref <- x13(y_new, spec_x13_ref)
sa_x13_ref


summary(sa_x13_ref)
end(y_raw)
```

#### Concl and Issues draft : ok set up 

- si period absent et rien, erreur 
- si period absent mais star and end renseignés: pas d'erreur mais RIEN ne se passe
- si period seul: erreur
- si period et start seul: erreur
- si period and seul: spec ok // mais estimation erreur (summary erreur: to detail)
- si period start end : si start avant end, ignores le start: ne fait rien, mais pas d'avertissement 
- si period end and start, corrects:
    - AO pas marques dans la ref_spec !! PRINT
    - estimation ok (AO posés ou on veut)
Q: JP estimation and fixed model ? (tout fixé,..coeffs contraints)


#### TPs (with T)

- print 
- warning 
- error massage 



### Outliers

```{r}
#| echo: true
#| eval: false
spec_x13_ref <- x13_refresh(
    current_result_spec, # point spec to be refreshed
    reference_spec, # domain spec (set of constraints)
    period=12,
    start=c(2000,1),
    end = c(2019,12),
    policy = "Outliers")
spec_x13_ref
sa_x13_ref <- x13(y_new, spec_x13_ref)
sa_x13_ref


summary(sa_x13_ref)
end(y_raw)
```

#### Concl and Issues draft 

- si period absent et rien: pas d'erreur mais ne garde pas les outliers de ref spec ??, mais garde bien les ordres arima 

- si period absent mais star and end renseignés: star et end ingnorés et pre-specified de ref spec ignores 


- si period seul: pas de reidentification !!! DOC + manque message 

- si period et start seul: reidentification à partir du start ok 


- si period and end seul: pas de reidentification 


- si period start end : 

-- start apres: ignore le end  ne fait rien, mais pas d'avertissement 

print: detection FROM même si end, from to
(voir les prints des spans)

- si period end and start, corrects:
    - pas de end dans le print
    - ignore le end !!!! I 
    
Q: JP estimation and fixed model ? (tout fixé,..coeffs contraints)

##### Issues



### Outliers stochastic component 

```{r}
#| echo: true
#| eval: false
spec_x13_ref <- x13_refresh(
    current_result_spec, # point spec to be refreshed
    reference_spec, # domain spec (set of constraints)
    period=12,
    start=c(2020,1),
    end = c(2022,4),
    policy = "Outliers_StochasticComponent")
spec_x13_ref
sa_x13_ref <- x13(y_new, spec_x13_ref)
sa_x13_ref


summary(sa_x13_ref)
end(y_raw)
```

#### Concl and Issues draft : ok 

- si period start end ok : 

-- arima reestimation ok 


print: detection FROM même si end, from to
(voir les prints des spans)

- si period end and start, corrects:
    - pas de end dans le print
    - ignore le end !!!! I et Doc (only from the time being)
    
### Freeparameters 

```{r}
#| echo: true
#| eval: false
spec_x13_ref <- x13_refresh(
    current_result_spec,
    reference_spec,
    policy="FixedAutoRegressiveParameters")
spec_x13_ref
sa_x13_ref <- x13(y_new, spec_x13_ref)
summary(sa_x13_ref)

```
```{r}

#| echo: true
#| eval: false
library("rjd3toolkit")
library("rjd3x13")
# specification for first estimation
spec_ts_1 <- x13_spec("rsa5")

y_raw<-rjd3toolkit::ABS$X0.2.05.10.M
# first estimation
sa_ts <- x13(y_raw, spec_ts_1) 
sa_ts

# specs to refresh
current_result_spec <- sa_ts$result_spec
reference_spec <- sa_ts$estimation_spec
spec_ts_ref <- x13_refresh(
    current_result_spec,
    reference_spec, 
    period=12,
    start=c(2017,1),
    end = c(2017,6),
    policy = "Current")
spec_ts_ref
sa_ts_ref <- x13(y_new, spec_ts_ref)
summary(sa_ts_ref)
```



#### Concl and Issues draft : ok 

- free parameters doesn't reestimate arima coeffs : true ? FALSE ok 
- free parameters inst the default: ok 

ISSUE set up
- print pb with arima coeffs : are printed as fixed in the specification in 
 "FixedParameters", "FixedAutoRegressiveParameters", "Freeparameters"
 print is ok in "Outliers_StochasticComponent", "Outliers"
 coeffs are set to zero 
 
 check in TS

