---
title: "T-rjd3tramoseats_refresh_tests"
format: html
---

# PB T solved in x12: same for TS ?

# Objectifs

- key reproducible format of testing (pre-vignette)
- the vignette

- end up with updated Fatih code and verif results in rjd3ws (not here)

## general 

- harmonize policies names 

## o1: one refresh qmd per concerned package 

- with issues


```{r}
#| label: loading-rjdverse
#| echo: true
#| eval: true
library("rjd3toolkit")
library("rjd3tramoseats")

```


```{r}
#| label: data import 
#| echo: true
#| eval: true
# Data  :
ipi <- read.csv2(
    "C:/Users/YWYD5I/Documents/00_RJD3_Developpement/RJD3_development/Data/IPI_nace4.csv"
)
ipi$date <- as.Date(ipi$date, format = "%d/%m/%Y")
ipi[, -1] <- sapply(ipi[, -1], as.numeric)
# creating a TS object from a data frame
y_raw <- ts(
    ipi[, "RF0812"],
    frequency = 12,
    start = c(1990, 1),
    end = c(2021, 12)
)
y_new <- ts(
    ipi[, "RF0812"],
    frequency = 12,
    start = c(1990, 1),
    end = c(2022, 9)
)

# start(y_raw)
end(y_raw)
# start(y_new)
end(y_new)

## add points for outlier detection 
window(y_new,start=c(2022,3), end=c(2022,5))<-c(51,52,53)


```






## first estimation and spec to be refreshed

```{r}
# specification for first estimation
spec_ts_1 <- tramoseats_spec("rsa5")
spec_ts_1 <-add_outlier(spec_ts_1, type = "AO",
                         date = c("2020-03-01","2020-04-01"))

# first estimation
sa_ts <- tramoseats(y_raw, spec_ts_1) # AO (2000,6) and TD (2000,7)
sa_ts

# def of specs to refresh

current_result_spec <- sa_ts$result_spec
reference_spec <- sa_ts$estimation_spec

```
# Tramo-seats PRINT pbs

- outliers

- seats PARAMS

ISSUE set up 

```{r}
#| echo: true
#| eval: true
library("rjd3toolkit")
library("rjd3tramoseats")
spec<-tramoseats_spec("rsafull")
spec <-set_seats(spec,
  fcasts = -3,
  bcasts = -3,
  bias = TRUE)
spec
```


same pbs in model print ? NO doesn't really make sense

```{r}
#| echo: true
#| eval: true
library("rjd3toolkit")
library("rjd3tramoseats")
spec<-tramoseats_spec("rsafull")
spec <-set_seats(spec,
  fcasts = -3,
  bcasts = -3,
  bias = TRUE)
spec
sa_ts<-tramoseats(rjd3toolkit::ABS$X0.2.09.10.M,spec)
sa_ts
summary(sa_ts)
```



### Fixed: FIXED

```{r}
#| echo: true
#| eval: false
library("rjd3toolkit")
library("rjd3tramoseats")
# specification for first estimation
spec_ts_1 <- tramoseats_spec("rsa5")

y_raw<-rjd3toolkit::ABS$X0.2.05.10.M
# first estimation
sa_ts <- tramoseats(y_raw, spec_ts_1) 
sa_ts

# specs to refresh
current_result_spec <- sa_ts$result_spec
reference_spec <- sa_ts$estimation_spec
spec_ts_ref <- tramoseats_refresh(
    current_result_spec,
    reference_spec, 
    policy = "Fixed")
spec_ts_ref
sa_ts_ref <- tramoseats(y_new, spec_ts_ref)
summary(sa_ts_ref)
```

### Fixed: Fixed parameters and CO (pb initial)

```{r}
#| echo: true
#| eval: false
library("rjd3toolkit")
library("rjd3tramoseats")
library("rjd3x13")
# specification for first estimation
spec_ts_1 <- tramoseats_spec("rsa5")
spec_x13_1 <- x13_spec("rsa5")
y_raw<-rjd3toolkit::ABS$X0.2.05.10.M
# first estimation
sa_ts <- tramoseats(y_raw, spec_ts_1) 
sa_x13<-x13(y_raw,spec_x13_1)

# refresh with tramoseats 
current_result_spec <- sa_ts$result_spec
reference_spec <- sa_ts$estimation_spec
spec_ts_ref <- tramoseats_refresh(
    current_result_spec,
    reference_spec, 
    policy = "FixedParameters")
spec_ts_ref

refresh with x13
current_result_spec <- sa_x13$result_spec
reference_spec <- sa_x13$estimation_spec
spec_x13_ref <- x13_refresh(
    current_result_spec,
    reference_spec, 
    policy = "FixedParameters")
spec_x13_ref


sa_ts_ref <- tramoseats(y_new, spec_ts_ref)
summary(sa_ts_ref)
```

# Test of period, start end parameters 

### Current

```{r}
#| echo: true
#| eval: false
library("rjd3toolkit")
library("rjd3tramoseats")

# specification for first estimation
spec_ts_1 <- tramoseats_spec("rsa5")

y_raw<-rjd3toolkit::ABS$X0.2.05.10.M
# first estimation
sa_ts <- tramoseats(y_raw, spec_ts_1) 
sa_ts

# specs to refresh
current_result_spec <- sa_ts$result_spec
reference_spec <- sa_ts$estimation_spec
spec_ts_ref <- tramoseats_refresh(
    current_result_spec,
    reference_spec, 
    period=12,
    start=c(2017,1),
    end = c(2017,6),
    policy = "Current")
spec_ts_ref
sa_ts_ref <- tramoseats(y_new, spec_ts_ref)
summary(sa_ts_ref)
```

#### Concl and Issues draft 

Issue set up 

- if `period` is missing and nothing else is specified, error message but not explicit enough
Error in if (end[2] == period) end <- c(end[1] + 1, 1) else end <- c(end[1],  : 
 argument length is zero 
  
Suggestion change to ERROR: With "policy = current", arguments `period`, `start` and `end` have to be specified"

- if `period` is missing but `start` and `end` are specified: no error, no warning, but NOTHING happens

Suggestion generate error and change message to ERROR: With "policy = current", arguments `period`, `start` and `end` have to be specified"

- if only `period` and `start` are specified: error but message could be improved 
Suggestion change to ERROR: With "policy = current", arguments `period`, `start` and `end` have to be specified"


- if only `period` and `end are specified: specification written but estimation will generate an error 

Suggestion generate error and change message to ERROR: With "policy = current", arguments `period`, `start` and `end` have to be specified"


- if `period` `start` and `end` but`start` is before `end`, ignores the `start`: no error nor warning and no refresh 

Suggestion generate error and change message to ERROR: With "policy = current", arguments `period`, `start` and `end` have to be specified"

- if `period` `end` and `start`, correctly specified
    - AO's are not printed in refreshed spec in the refreshed spec 
    
see code below to generate all those cases 


    
    
    
Q: JP estimation and fixed model ? (tout fixé,..coeffs contraints)

##### Issues


#### TPs (with T) à programmer

- print 
- warning 
- error massage 
# current meant to be: AO on NEW data points, or in fact from date ?


### Outliers

```{r}
#| echo: true
#| eval: false
spec_ts_ref <- tramoseats_refresh(
    current_result_spec, # point spec to be refreshed
    reference_spec, # domain spec (set of constraints)
    period=12,
    start=c(2000,1),
    # end = c(2019,12), # ignored as in x13: ok 
    policy = "Outliers")
spec_ts_ref
sa_ts_ref <- tramoseats(y_new, spec_ts_ref)
sa_ts_ref


summary(sa_ts_ref)
end(y_raw)
```

#### Concl and Issues draft 

ok

- dans TS pb de print: outliers is enabled: NO (tjs)

- si period absent et rien: pas d'erreur mais ne garde pas les outliers de ref spec ??, mais garde bien les ordres arima 

- si period absent mais stat and end renseignés: star et end ingnorés et pre-specified de ref spec ignores 


- si period seul: pas de reidentification !!! DOC + manque message 

- si period et start seul: reidentification à partir du start ok 


- si period and end seul: pas de reidentification 


- si period start end : 

-- start apres: ignore le end  ne fait rien, mais pas d'avertissement 

print: detection FROM même si end, from to
(voir les prints des spans)

- si period end and start, corrects:
    - pas de end dans le print
    - ignore le end !!!! I 

- print dans tramo manque les fixe/ initial comme dans x13

##### Issues



### Outliers stochastic component 

```{r}
#| echo: true
#| eval: false
spec_ts_ref <- tramoseats_refresh(
    current_result_spec, # point spec to be refreshed
    reference_spec, # domain spec (set of constraints)
    period=12,
    start=c(2020,1),
    # end = c(2022,4),
    policy = "Outliers_StochasticComponent")
spec_ts_ref
window(y_new, start=c(1999,2),end=c(1999,2))<-12
sa_ts_ref <- tramoseats(y_new, spec_ts_ref)
sa_ts_ref


summary(sa_ts_ref)
end(y_raw)
```

#### Concl and Issues draft 

- si period start end ok : 

-- arima reestimation ok 


print: detection FROM même si end, from to
(voir les prints des spans)

- si period end and start, corrects:
    - pas de end dans le print
    - ignore le end !!!! I et Doc (only from the time being)
    
dans TS avec outliers stoch comp  ISSUE 
il n'affiche les pre-speciified dans la spec avant le start
et il redecte (si on ajoute oulier avant comp il le voit)
    
TS and X13 classer les ouliers par date dans 
- print spec 

##### Issues

