---
title: "rjd3toolkit_Distributions"
format: html
---


Distributions

PDFs, CDFs and inverses

density_chi2() cdf_chi2() random_chi2()
Chi-Squared Distribution
density_gamma() cdf_gamma() random_gamma()
Gamma Distribution
density_inverse_gamma() cdf_inverse_gamma() random_inverse_gamma()
Inverse-Gamma Distribution
density_inverse_gaussian() cdf_inverse_gaussian() random_inverse_gaussian()
Inverse-Gaussian Distribution
density_t() cdf_t() random_t()
Student Distribution 


## Student

native R from \url{https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/TDist}

```{r}

# Probability density function of T with 2 degrees of freedom

# Toolkit 
z <- density_t(df = 2, .01 * seq(-100, 100, 1))
plot(z)

# Native R
zr<- dt(x=.01 * seq(-100, 100, 1), df=2, log = FALSE)
plot(zr)

# Generating a random vector with each component drawn from a T(2) distribution
z <- random_t(120, 100)
plot(z)

# Native R
zr<-rt(n=100, df=12)
plot(zr)
 
# Computing the probability that the random variable X following a T distribution
# with df degrees of freedom is lower than x
z <- cdf_t(df = 12, x = 1.2)
z

# native R

#pt(q, df, ncp, lower.tail = TRUE, log.p = FALSE)
# pt= cdf
zr<-pt(1.2,12)
zr # ok 

z <- cdf_t(df = 12, x = c(0:10)) # array of values
z

# pas de inverse cdf for student dans toolkit 
# qt = inverse cdf qt(p, df, ncp, lower.tail = TRUE, log.p = FALSE)
q<- qt(0.95,30)

q
```

```{r}


# NOT RUN {
require(graphics)

1 - pt(1:5, df = 1)
qt(.975, df = c(1:10,20,50,100,1000))

tt <- seq(0, 10, len = 21)
ncp <- seq(0, 6, len = 31)
ptn <- outer(tt, ncp, function(t, d) pt(t, df = 3, ncp = d))
t.tit <- "Non-central t - Probabilities"
image(tt, ncp, ptn, zlim = c(0,1), main = t.tit)
persp(tt, ncp, ptn, zlim = 0:1, r = 2, phi = 20, theta = 200, main = t.tit,
      xlab = "t", ylab = "non-centrality parameter",
      zlab = "Pr(T <= t)")

plot(function(x) dt(x, df = 3, ncp = 2), -3, 11, ylim = c(0, 0.32),
     main = "Non-central t - Density", yaxs = "i")
# }
```


## CHi2

add native R 

native R from \url{https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/Chisquare}

```{r}

# Probability density function for a Chi-Square distribution with 3 degrees of freedom.
z <-density_chi2(df = 3,.01 * seq(-100, 100, 1))
plot(z)
# native R
zr<-dchisq(.01 * seq(-100, 100, 1), df=3, ncp = 0, log = FALSE)
plot(zr)
# ok


# Computing the probability that the random variable X following a Chi-Square distribution
# with df degrees of freedom is lower than x
z<-cdf_chi2(df = 3, 1:10)
z

# native r
zr<- pchisq(1:10, df=3, ncp = 0, lower.tail = TRUE, log.p = FALSE)
zr

# inverse cdf pour quantiles, not in toolkit
qchisq(p, df, ncp = 0, lower.tail = TRUE, log.p = FALSE)


# Generating a random vector with each component drawn from a Chi-square distribution
# with df degrees of freedom 
z <- random_chi2(df = 3, n = 10)
z

# native R
rchisq(n=10, df=3, ncp = 0)

```

## Gamma dsitribution: PB results 

add native R 

native R from \url{https://www.rdocumentation.org/packages/Rlab/versions/4.5.1/topics/Gamma}

```{r}
#' density_gamma(shape = 1, scale = 2, x = 1:10)
#' cdf_gamma(shape = 1, scale = 2, x = 1:10)
#' 


# Probability density function for a Gamma distribution
z <-density_gamma(shape = 7.5, scale =0.5 , x=.001 * seq(0, 300, 1))
plot(z)


# native R
zr<-dgamma(dgamma(x, alpha = 7.5, beta = 0.5)
plot(zr)

# TO CHECK


# Computing the probability that the random variable X following a Gamma distribution
# with shape 1 and scale 2 is lower than x
z<-cdf_gamma(shape = 1, scale = 2, x = 1:10)
z

# native r
zr<- pchisq(1:10, df=3, ncp = 0, lower.tail = TRUE, log.p = FALSE)
zr

## gamma 
# inverse cdf pour quantiles, not in toolkit
qchisq(p, df, ncp = 0, lower.tail = TRUE, log.p = FALSE)


# Generating a random vector with each component drawn from a Gamma distribution
# with shape 1 and scale 2
z<- random_gamma(shape = 1, scale = 2, n = 10)
z

# native R
rchisq(n=10, df=3, ncp = 0)


```
## Inverse gamma 

add native R 

native R from \url{https://www.rdocumentation.org/packages/nimble/versions/1.4.1/topics/Inverse-Gamma}

```{r}

#' density_inverse_gamma(shape = 1, scale = 2, x = 1:10)
#' cdf_inverse_gamma(shape = 1, scale = 2, x = 1:10)
#' random_inverse_gamma(shape = 1, scale = 2, n = 10)
#' 
#' # Probability density function for an Inverse Gamma distribution
z <-density_inverse_gamma(shape = 1, scale = 2,x=.001 * seq(0, 300, 1))
plot(z)

# Computing the probability that the random variable X following an Inverse Gamma distribution
# with shape 1 and scale 2 is lower than x
z<-cdf_inverse_gamma(shape = 1, scale = 2, x = 1:10)
z

# Generating a random vector with each component drawn from an Inverse Gamma distribution
# with shape 1 and scale 2
z<- random_inverse_gamma(shape = 1, scale = 2, n = 10)
z

```
## Inverse gaussian: check results 



```{r}
dinvgauss(y, m, s, log=FALSE)
pinvgauss(q, m, s)
qinvgauss(p, m, s)
rinvgauss(n, m, s)


dinvgauss(y=5, 5, 1)
pinvgauss(5, 5, 1)
qinvgauss(0.8, 5, 1)
rinvgauss(10, 5, 1)

#' density_inverse_gaussian(shape = 1, scale = 2, x = 1:10)
#' random_inverse_gaussian(shape = 1, scale = 2, n = 5)
#' 
#' # Probability density function for an Inverse Gaussian distribution
z <-density_inverse_gaussian(shape = 1, scale = 2, x = 0.1* 0:30)
plot(z)

# # Computing the probability that the random variable X following an Inverse Gaussian distribution
# # with shape 1 and scale 2 is lower than x
# z<-cdf_inverse_gamma(shape = 1, scale = 2, x = 1:10)
# z

# Generating a random vector with each component drawn from an Inverse Gaussian distribution
# with shape 1 and scale 2
z<-random_inverse_gaussian(shape = 1, scale = 2, n = 5)
z



```


